---
title: "__COVID-19 cases and deaths for selected countries and months__"
author: "Stephanie de Wit"
date: "_`r Sys.Date()`_"
output: 
  pdf_document:
    extra_dependencies: ["float"]
params:
  country: "Netherlands"
  year: 2022
  month: 3
---

### Data 

This report has been written to represent the [public data](https://www.ecdc.europa.eu/en/publications-data/data-daily-new-cases-covid-19-eueea-country) on COVID-19 cases and deaths as published by the European Center for Disease Prevention and Control (ECDC). 

```{r, include = FALSE}
library(tidyverse)
library(utils)
library(scales)

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

data <- read.csv("https://opendata.ecdc.europa.eu/covid19/nationalcasedeath_eueea_daily_ei/csv", na.strings = "", fileEncoding = "UTF-8-BOM")
```

```{r, include = FALSE}
# Filteren op parameters:
data_plot <- data %>% filter(countriesAndTerritories == params$country, year == params$year, month == (params$month - 1) | month == params$month | month == (params$month + 1))
```

```{r, include = FALSE}
# Objects voor land, jaartal, maanden en titels aanmaken:
country <- params$country
year <- params$year

if(params$month == 1){month <- "January"}
if(params$month == 2){month <- "February"}
if(params$month == 3){month <- "March"}
if(params$month == 4){month <- "April"}
if(params$month == 5){month <- "May"}
if(params$month == 6){month <- "June"}
if(params$month == 7){month <- "July"}
if(params$month == 8){month <- "August"}
if(params$month == 9){month <- "September"}
if(params$month == 10){month <- "October"}
if(params$month == 11){month <- "November"}
if(params$month == 12){month <- "December"}

if((params$month - 1) == 1){month_b <- "January"}
if((params$month - 1) == 2){month_b <- "February"}
if((params$month - 1) == 3){month_b <- "March"}
if((params$month - 1) == 4){month_b <- "April"}
if((params$month - 1) == 5){month_b <- "May"}
if((params$month - 1) == 6){month_b <- "June"}
if((params$month - 1) == 7){month_b <- "July"}
if((params$month - 1) == 8){month_b <- "August"}
if((params$month - 1) == 9){month_b <- "September"}
if((params$month - 1) == 10){month_b <- "October"}
if((params$month - 1) == 11){month_b <- "November"}
if((params$month - 1) == 12){month_b <- "December"}

if((params$month + 1) == 1){month_a <- "January"}
if((params$month + 1) == 2){month_a <- "February"}
if((params$month + 1) == 3){month_a <- "March"}
if((params$month + 1) == 4){month_a <- "April"}
if((params$month + 1) == 5){month_a <- "May"}
if((params$month + 1) == 6){month_a <- "June"}
if((params$month + 1) == 7){month_a <- "July"}
if((params$month + 1) == 8){month_a <- "August"}
if((params$month + 1) == 9){month_a <- "September"}
if((params$month + 1) == 10){month_a <- "October"}
if((params$month + 1) == 11){month_a <- "November"}
if((params$month + 1) == 12){month_a <- "December"}

cases_b <- paste("COVID-19 cases for", country, "in", month_b, year)
cases <- paste("COVID-19 cases for", country, "in", month, year)
cases_a <- paste("COVID-19 cases for", country, "in", month_a, year)

deaths_b <- paste("COVID-19 deaths for", country, "in", month_b, year)
deaths <- paste("COVID-19 deaths for", country, "in", month, year)
deaths_a <- paste("COVID-19 deaths for", country, "in", month_a, year)
```

### COVID-19 cases

The three graphs below depict the number of new COVID-19 cases as measured per day for the chosen month, the previous month and the following month.

```{r, fig.cap = cases_b, echo = FALSE, fig.pos = "H", fig.align = "center", out.width = "80%"}
data_plot %>% filter(month == (params$month - 1)) %>% ggplot(aes(x = day, y = cases)) +
  geom_point(size = 2, color = "orange") +
  labs(title = paste("COVID-19 cases for", country, "in", month_b, year), x = "Day", y = "New COVID-19 cases") +
  scale_y_continuous(labels = comma, limits = c(0, max(data_plot$cases))) +
  scale_x_continuous(limits = c(1, 31)) +
  theme_bw()
```

```{r, fig.cap = cases, echo = FALSE, fig.pos = "H", fig.align = "center", out.width = "80%"}
data_plot %>% filter(month == params$month) %>% ggplot(aes(x = day, y = cases)) +
  geom_point(size = 2, color = "orange") +
  labs(title = paste("COVID-19 cases for", country, "in", month, year), x = "Day", y = "New COVID-19 cases") +
  scale_y_continuous(labels = comma, limits = c(0, max(data_plot$cases))) +
  scale_x_continuous(limits = c(1, 31)) +
  theme_bw()
```

```{r, fig.cap = cases_a, echo = FALSE, fig.pos = "H", fig.align = "center", out.width = "80%"}
data_plot %>% filter(month == (params$month + 1)) %>% ggplot(aes(x = day, y = cases)) +
  geom_point(size = 2, color = "orange") +
  labs(title = paste("COVID-19 cases for", country, "in", month_a, year), x = "Day", y = "New COVID-19 cases") +
  scale_y_continuous(labels = comma, limits = c(0, max(data_plot$cases))) +
  scale_x_continuous(limits = c(1, 31)) +
  theme_bw()
```

### COVID-19 deaths

The three graphs below depict the amount of COVID-19 deaths as measured per day for the chosen month, the previous month and the following month.

```{r, fig.cap = deaths_b, echo = FALSE, fig.pos = "H", fig.align = "center", out.width = "80%"}
data_plot %>% filter(month == (params$month - 1)) %>% ggplot(aes(x = day, y = deaths)) +
  geom_point(size = 2, color = "red") +
  labs(title = paste("COVID-19 deaths for", country, "in", month_b, year), x = "Day", y = " New COVID-19 deaths") +
  scale_y_continuous(labels = comma, limits = c(0, max(data_plot$deaths))) +
  scale_x_continuous(limits = c(1, 31)) +
  theme_bw()
```

```{r, fig.cap = deaths, echo = FALSE, fig.pos = "H", fig.align = "center", out.width = "80%"}
data_plot %>% filter(month == params$month) %>% ggplot(aes(x = day, y = deaths)) +
  geom_point(size = 2, color = "red") +
  labs(title = paste("COVID-19 deaths for", country, "in", month, year), x = "Day", y = "New COVID-19 deaths") +
  scale_y_continuous(labels = comma, limits = c(0, max(data_plot$deaths))) +
  scale_x_continuous(limits = c(1, 31)) +
  theme_bw()
```

```{r, fig.cap = deaths_a, echo = FALSE, fig.pos = "H", fig.align = "center", out.width = "80%"}
data_plot %>% filter(month == (params$month + 1)) %>% ggplot(aes(x = day, y = deaths)) +
  geom_point(size = 2, color = "red") +
  labs(title = paste("COVID-19 deaths for", country, "in", month_a, year), x = "Day", y = "New COVID-19 deaths") +
  scale_y_continuous(labels = comma, limits = c(0, max(data_plot$deaths))) +
  scale_x_continuous(limits = c(1, 31)) +
  theme_bw()
```
